The paper on \Large \bf Blockchain Frontrunning

### 2018-08-27 frontrunning/Latex/sections/paper.tex
[frontrunning] related work breidenbach2018enter

 ~\cite{breidenbach2018enter}

@@

\emph{Fixed transaction ordering}: One possible solution to fix current blockchains in regards to transaction reordering by miners has been proposed by da Silva et al~\cite{fixedordering2018silva}, which consist of an algorithm, Fixed Transaction Ordering and Admission (FTOA) algorithm, in the consensus protocol that enforces the order of the transactions.

@@

%TODO: also fixes collatorize the commit, but what about no collatorization cases but hide the participation (not really a front-running case)
\item{\textbf{Submarine sends}: describe. General solution similar to commit and reveal. This is to solve the participatory factor of the commit and reveal solution.}

>>>>

Breidenbach~\etal ~\cite{breidenbach2018enter} face the front-running issue in the context of automating bug bounties for smart contracts. Upon submitting the bug bounty to the Hydra smart contract, one can front-run the bug report and claim the bounty instead of the original reporter. They propose \textit{Submarine Commitments} which is to conceal the bounty claim and the participatory factor. They claim submarine commitments ``are a stronger form of a commit-reveal scheme''.

@@

\emph{Fixed transaction ordering}: One possible solution to fix current blockchains in regards to transaction reordering by miners has been proposed by da Silva~\etal~\cite{fixedordering2018silva}, which consist of an algorithm, Fixed Transaction Ordering and Admission (FTOA) algorithm, in the consensus protocol that enforces the order of the transactions.

@@

%TODO: also fixes collatorize the commit, but what about no collatorization cases but hide the participation (not really a front-running case)
\item{\textbf{Submarine Commitments}: describe. General solution similar to commit and reveal. This is to solve the participatory factor of the commit and reveal solution.}
